outline

### 2019-11-28 Rmd/discussion.Rmd
updated methods text
updated intro

@@

Our measures of students' self-confidence in research ability was merely subjective. In future iterations of our framework, we would like to measure systematic and objective outcomes. One strategy for implementing this is to administer a survey, such as \_\_\_, both before and after the mentored research project. We would use validated survey questions that focused on student beliefs about themselves and their skills.

@@

>>>>

1. build self-confidence, self-assessed proficiency in data analysis and statistics

1. greater interest in quantitative careers and/or grad school in quant fields

1. Working with real data to solve real scientific questions

1. Learn by example interplay between data science (statistics) and science research

@@

Our measures of students' self-confidence in research ability was merely subjective. In 
future iterations of our framework, we would like to measure systematic and objective 
outcomes. One strategy for implementing this is to administer a survey, such as \_\_\_, 
both before and after the mentored research project. We would use validated survey 
questions that focused on student beliefs about themselves, their skills, and their 
future careers. **maybe list resources for such survey questions**

@@

1. assessment of attitudes (pre and post survey??)

1. survey questions might include those from @vance2017eight. I have the survey as a pdf in mendeley. It is part of the supp info for @vance2017eight.

### 2019-11-28 Rmd/introduction.Rmd
updated intro

- big data
- new areas of application of statistical methods - social media
- need for mentoring 
- need for students to work with real data
- motivate statistical analysis and statistics research by real world scientific research questions (Box 1976)

@nolan2010computing

@@

Social media data, including tweets from Twitter and posts from Facebook, are 
available through website application product interfaces (APIs). Twitter 
shares, via a streaming API, a sample of approximately one percent of all 
tweets during an API query time period. Researchers have studied tweets for a 
variety of purposes, including 
inference of relationships and social networks among users [@lin2011joint]; determination of 
authorship of specific tweets when multiple persons use a single account [@drob]; and 
study of rhetoric in recruiting political supporters [@pelled2018little,@wells2016trump].

>>>>

- big data
- new areas of application of statistical methods - social media
- need for students to work with real data
- motivate statistical analysis and statistics research by real world scientific research questions (Box 1976)
- need for mentoring

@@

Social media data, including tweets from Twitter and posts from Facebook, are 
available through website application product interfaces (APIs). Twitter 
shares, via a streaming API, a sample of approximately one percent of all 
tweets during an API query time period [@tweet_stream]. 
Researchers have studied tweets for a 
variety of purposes, including 
inference of relationships and social networks among users [@lin2011joint]; 
determination of 
authorship of specific tweets when multiple persons share a single account [@drob]; and 
study of rhetoric in recruiting political supporters [@pelled2018little,@wells2016trump]. 
Recognizing the potential utility of tweets for data science research, we created a 
collection of tweets over time by repeated querying of the Twitter streaming API.

@nolan2010computing fervently argue for students to work with real data. 
Working with real data allows them to develop skill not only in statistical analysis,
but also in data transfer from online sources, in data storage, and in using data 
from multiple file formats. In the case of Twitter data, tweets are stored in
Javascript Object Notation (JSON) [@tweet_json, @json].

A key component of our mentoring framework is the emphasis on using real data to answer real 
scientific questions. We believe that this process develops the problem-solving skills that 
students will need in their future careers in data science.

We encouraged the student to articulate a scientific research question, translate that question into quantitative and statistical terms, determine which data could be used to address the question, acquire the data, analyze data, visualize results, and communicate what they learned.

**Need to explain above paragraph with our two student examples. What types of questions did they articulate? How did they translate to quant terms? How did they determine data availability? etc.**

### 2019-11-28 Rmd/jse-2019-ms.Rmd
updated ms Rmd and bib file
updated intro

---
title: 'A framework for mentored data science research'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
output: 
  - github_document
  - pdf_document
---

>>>>

---
title: 'A framework for undergraduate data science research'
author: "Frederick J. Boehm and Bret M. Hanlon"
date: "8/20/2019"
params:
  lastmod: !r lubridate::now()
bibliography: jse.bib
output: 
  - github_document
  - bookdown::pdf_document2
  - bookdown::html_document2
---

### 2019-11-28 Rmd/outline.Rmd
updated ms Rmd and bib file
updated intro

---
title: "outline"
author: "Frederick J. Boehm"
date: "11/20/2019"
output: github_document
---

@@

Mimic, maybe, the DTL2010 article in organization of the intro. have a subsection on *four* key components (vs DTL's three key components). These are the three of DTL plus reproducible research practices.

>>>>

---
title: "outline"
author: "Frederick J. Boehm"
date: "11/20/2019"
output: bookdown::html_document2
---

@@

Mimic, maybe, the DTL2010 article in organization of the intro.

~~have a subsection on *four* key components (vs DTL's three key components). These are the three of DTL plus reproducible research practices.~~
